### 2015-10-10 README.Rmd
updated readme. still needs work

```{r}
library(qmj)
data(companies) #Stores company names and tickers from the Russell 3000 index
data(financials) #Stores financial documents for the given list of companies.
data(prices) # Stores price returns and closing stock prices for the past two years.
data(quality) #Stores the quality scores and the scores of its components.

#And more detailed data sets into what makes up quality
data(profitability)
data(growth)
data(payouts)
data(safety)
```

@@

This will return a numeric vector containing profitability z-scores for the given companies, where the nth number corresponds to the nth company.

##Analyzing Your Data
The qmj package has stored a large number of qmj objects, which store significant amounts of information about a single company and which allows more in-depth analysis of that company. Some examples of analysis follow:

```{r}
data(qmjs)
first_qmj <- qmjs[[1]]
summarize(first_qmj) # Displays key information about this qmj object.

#We're clearly missing some interesting data, but we can still 
#perform some analysis.
data(safety)
```
```{r fig.width=7, fig.width=6}
plot_safety(first_qmj, safety)
```

```{r}
#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]
```
```{r fig.width=7, fig.height=6}
plot_quality(second_qmj, quality)
```

```{r}
#What if I'm only interested in looking closely at a few companies? 
#Well, voila.
desired_companies <- c("GOOG", "IBM", "FLWS") #Returns a list containing the given qmj objects in order.
desired_qmjs <- get_qmjs(desired_companies, qmjs)

summarize(desired_qmjs[[1]])
```

But the package also provides some tools for better examining your data en masse, as opposed to individual companies.

```{r}
#Let's look at the head of our quality data frame.
data(quality)
head(quality)

#Angies has an abnormally high growth score, which is very suspicious.
#Companies that are primarily driven by a single component score 
#are suspect, so let's filter out companies that are driven by growth.
sans_growth <- filter_companies(quality, filter="growth")
head(sans_growth)

#On the other hand, if we're interested in only companies that are 
#driven by growth, we can do the following:
driven_by_growth <- filter_companies(quality, filter="growth", remove=FALSE, isolate=TRUE)
head(driven_by_growth)

#We can also remove all companies with quality scores which are 
#primarily driven by any component.
#Notice that the remove parameter is by default TRUE, and 
#isolate is by default FALSE
liberal_arts_companies <- filter_companies(quality, filter="all")
head(liberal_arts_companies)
```

@@

The get_prices function is able to save its progress as it temporarily saves its download data to the extdata folder in the package's folder.

>>>>

```{r}
library(qmj)
data(companies) #Stores company names and tickers from the Russell 3000 index
data(financials) #Stores financial documents for the given list of companies.
data(prices) # Stores price returns and closing stock prices for the past two years.
data(quality) #Stores the quality scores and the scores of its components.
```

@@

This will return a data frame containing profitability z-scores for the given companies as well as the z-scores for the components creating the profitability scores.

@@

Similar to the get_info function, The get_prices function is also able to save its progress and resume previous downloads.
